---
title: "Extracting tags from tagsets"
author: "Will Lowe, Jakob Willisch and Nicole Baerg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extracting tags from tagsets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Extracting annotations

Load the package
```{r}
library(xmlAnnotate)
```
and load up some test data.
```{r}
folder <- system.file("extdata", "fomc", package = "xmlAnnotate")
dir(folder)
```

Extract the 'hedge' tags from the first file in that folder
```{r}
f <- file.path(folder, "2004_03_2-1.xml")
f
ftags <- get_tagset(f)
```
and take a look
```{r, echo=FALSE, results='asis'}
knitr::kable(ftags)
```

By default this function get `hedge` tags only.  So the call above is equivalent to 
```{r,eval=FALSE}
ftags <- get_tagset(f, nodes=c('hedge'))
```
We can have the `note` tags too, by adding it
```{r}
ftags2 <- get_tagset(f, nodes=c('hedge', 'note'))
```
which looks like
```{r, echo=FALSE, results='asis'}
knitr::kable(ftags2)
```

And if we want these tags extracted from all the XML files in a folder
```{r}
fftags <- get_tagsets(folder, nodes=c('hedge', 'note'))
```
This rowbinds the results from all the files it finds.

## Match Tags

If we want to extract all tags but want to match the  `word` and `note` tags to the `hedge` tag based on their positions in the text

```{r}
fftag <- get_tagset(f, nodes=c('hedge','word', 'note'))

fftag2 <- match_nodes(fftag, match_x = "hedge", match_y = c("word","note"))
```
which looks like
```{r, echo=FALSE, results='asis'}
knitr::kable(fftag2)
```
